---
title: "Tagging status update"
author: "Ian Gow"
date: "2015-09-11"
output: pdf_document
---
```{r tidy_function, include=FALSE} 
Sys.setenv(PGHOST="iangow.me", PGDATABASE="crsp")
library(dplyr)
tidy_count <- function(df) {
    df %>% 
        summarize(count=n()) %>%
        collect() %>%
        as.integer() %>%
        formatC(big.mark = ",")
}
```


```{r get_data, include=FALSE, cache=FALSE}

pg <- src_postgres()

equilar_fyrs <- tbl(pg, sql("
    SELECT DISTINCT director.equilar_id(company_id), fy_end
    FROM director.co_fin"))

directors <- tbl(pg, sql("
    SELECT DISTINCT director.equilar_id(director_id),
        director.director_id(director_id), director, fy_end
    FROM director.director"))

bio_data <- tbl(pg, sql("
    SELECT equilar_id, (director_id).director_id, fy_end, director, bio
    FROM director_bio.bio_data"))

proxy_filings <- tbl(pg, sql("
    SELECT equilar_id, fy_end,
        bool_or(cik IS NOT NULL) AS has_ciks,
        bool_or(file_name IS NOT NULL) AS has_proxies
    FROM director.equilar_proxies
    GROUP BY equilar_id, fy_end"))

tagged_firm_years <-
    bio_data %>%
    select(equilar_id, fy_end) %>%
    distinct()

tagging_issues <- tbl(pg, sql("
    SELECT DISTINCT equilar_id, fy_end, TRUE AS tagging_issue
    FROM director_bio.tagging_issues
    INNER JOIN director.equilar_proxies
    USING (file_name)
    WHERE file_name IS NOT NULL"))

untagged_firm_years <-
    equilar_fyrs %>%
    anti_join(tagged_firm_years) %>%
    left_join(proxy_filings) %>%
    left_join(tagging_issues) %>%
    mutate(tagging_issues=!is.na(tagging_issue),
           no_cik=is.na(has_ciks) | ! has_ciks,
           no_proxy= has_ciks & (is.na(has_proxies) | !has_proxies))
```

There are `r tidy_count(equilar_fyrs)` firm-years on Equilar. 
Of these, `r tidy_count(tagged_firm_years)` have at least one tagged bio, and
`r tidy_count(untagged_firm_years)` have none. 
Of the untagged firm-years, 
`r tidy_count(untagged_firm_years %>% collapse() %>% filter(no_cik))` have no matching
CIK, `r tidy_count(untagged_firm_years %>% collapse() %>% filter(no_proxy))` have CIKs, but no proxy filings, and a further
`r tidy_count(untagged_firm_years %>% collapse() %>% filter(tagging_issues))` have tagging issues.
This leaves a further, `r tidy_count(untagged_firm_years %>% collapse() %>% filter(!tagging_issues & !no_proxy & ! no_cik))` that have no obvious issues, but are untagged.


```{r tagged_bios, include=FALSE, cache=FALSE}
bios_tagged_firms <- tagged_firm_years %>%
    inner_join(directors) %>%
    left_join(bio_data) %>%
    left_join(tagging_issues) %>%
    collect() %>%
    mutate(has_bio = !is.na(bio),
           tagging_issues = !is.na(tagging_issue)) 
```

For the tagged firm-years, there are `r tidy_count(bios_tagged_firms)` to be tagged.\footnote{I ignore the small number of cases with "directors needing disambiguation".}
Of these, we have `r tidy_count(bios_tagged_firms %>% collapse() %>% filter(has_bio))` bios tagged, and
`r tidy_count(bios_tagged_firms %>% filter(!has_bio))` untagged.
For the untagged bios, we have tagging issues identified for filings associated with 
`r tidy_count(bios_tagged_firms %>% filter(!has_bio & tagging_issues))` of them, and no tagging issues flagged for the remaining `r tidy_count(bios_tagged_firms %>% filter(!has_bio & !tagging_issues))` of them.
